### 2018-08-21 paper.tex
Initialization

\documentclass[11pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage[font={small,it}]{caption}
\usepackage{fancyvrb}
\title{Analysis \& Visualization of Call Center Data using Python}
\author{John D. Bulger
\\
Karl Schmitt, PhD. (Advisor)
\\
Valparaiso University\\
}
\date{August 10, 2018}
\begin{document}
\maketitle

\begin{abstract}
\textit{The city of South Bend, Indiana operates a call center that serves as a primary point of contact for citizens.  The call center handles topics for nearly all of the city's departments.  An open data portal, maintained by the city, contains several years worth of information.  An analysis of this data was conducted using Python 3.6.  The data was 
analyzed for patterns by time of year, department, and topics with varying methods.  The cleaned, manipulated, and explored data was then developed into an 
interactive dashboard using the Bokeh library.  In doing so, an interactive HTML file will be distributed to the city, which can then be utilized, modified, and possibly connected 
directly to the data source}.
\end{abstract}

\section{Introduction}
The city of South Bend, located in northern Indiana, established a citizen-accessible call center in February 2013.  The call center handles calls from citizens regarding almost every aspect of city interaction, including waste pick-up and removal, water billing and disconnections, 
and code enforcement.  By serving as a central hub for communication, the call center is able to consolidate much of the data regarding citizen/consumer issues.  
Much of this data is available on South Bend's open data portal at \href{https://data-southbend.opendata.arcgis.com}{https://data-southbend.opendata.arcgis.com}.  The guiding questions for this analysis included seeking patterns and statistics on call volume and duration by timeframe, department, and topics.  The city has used several services/formats for data collection, resulting in data sets from differing time periods having different attributes and formats.  For most of the in-depth topic analysis, the most current format was used.

	\subsection{Prior Work}

	\subsection{Goals \& Desired Results}

\section{Methods}

%Overview of data and Python here.

	\subsection{Loading Data}

	\subsection{Cleaning Data}

	\subsection{Data Preprocessing}

	\subsection{Discuss packages and analysis plan of attack???}

\section{Analysis}

	\subsection{Calls by Month}

	\subsection{Calls by Day}

	\subsection{Calls by Department}

	\subsection{Calls by Topic}

	\subsection{Final Dashboard}

\section{Discussion}

\section{Conclusions}

In summary, this analysis and presentation of data trends can be viewed as a successful high-level exploration.  Trends and points emerged from this analysis that will surely be of interest to call center management, while more insights can surely be found while interacting with the visualization dashboard.  For the city, this study should serve to identify areas of business interest within the context of these findings, which could then warrant further exploration with more specific questions.  For example, the city may want to see day-of-week trends for a specific topic, or they may seek to see how the number of calls queued relate to the number of calls abandoned.  These more specific questions would necessarily arise from a specific business need, which could perhaps be identified from this study.

	\subsection{Opportunities for Further Work}

Several paths for further work on this topic exist; however, the exact approach depends on the city's desires.  One approach would be to obtain staffing and scheduling information for the call center and use simulation and optimization techniques to evaluate staffing levels and efficiency.  Another approach would be to develop another dashboard, or perhaps modify the current one, to interact directly with the call center's data source.  This would allow a live, current view of trending topics and departments.  Such a tool could allow call center management to be agile and preemptive regarding emerging trends.

\begin{thebibliography}{6}

\bibitem{}

\end{thebibliography}

\includepdf[pages=-]{311CallCenterDashboard}

\end{document}

### 2018-08-22 paper.tex
Link

@@
 
+After completion of the above analysis, the final dashboard was constructed.
+Each chart in this dashboard stems from a question or interest identified by the city analysts.
+The Bokeh package was used to create interactive visualizations, and allowed the final product to be conveniently packaged into a HTML file and sent to the call center management.
+In all, the dashboard includes visualizations of:
+
+\begin{itemize}
+  \item{Pie chart of total call time by department}
+  \item{Histogram of call volume by day of week, overlaid, with legend providing hide/show capabilities}
+  \item{Bar chart of topics with longest average call duration}
+  \item{Bar chart of topics with shortest average call duration}
+  \item{Jitterplot of call volume by topic within top departments}
+  \item{Bar chart of call volume by month}
+\end{itemize}
+
+These charts all utilize various implementation of Bokeh tools, such as HoverTool, BoxZoom, Pan, and checkbox interactivity.
+By incorporating these interactions into the dashboard, the result is a more dynamic, engaging product that is simple to interact with for employees outside of the technical fields.
+An image of the final dashboard can be found at the end of this paper, while a live link can be followed \href{https://jdbul33.github.io/311_Call_Dashboard.html}{here}.
+
 \section{Discussion}

### 2018-08-27 paper.tex
test terminal
preprocessing

@@
 
-%Overview of data and Python here.
+The data to be analyzed was acquired in three distinct comma-separated value files.
+Two of the files are publicly available, and are also posted on the \href{https://github.com/jdbul33/verbose-chainsaw}{Github repository} for this project.
+The third file was received directly from the city of South Bend, and as a result is not posted publicly at this time.
+\par
+The first file, referred to as the daily data, contains a daily summary of the call center data from the years 2013-2015.
+It is organized with 637 records indexed by date, with each record containing information such as the number of calls presented, average wait time, average number of calls in queue, and number of abandoned calls for that day.
+\par
+The second file, referred to as the case data, contains 488,601 rows of individual call data from 2013 through 2015.
+Calls were logged anonymously with data such as date, duration, topic, and department.
+This data format went obsolete when the current call system was implemented.
+\par
+The third file, referred to as the topic data, is the storage method of the current phone system in use by the city.
+This file contains 202,500 call records from 2016-2018.
+It contains much of the same attributes as the case data, but it is standardized to reflect the city's use of knowledge base articles.
+These articles correspond to possible questions or issues raised by callers; as a result, the call center employees have a reference to answer questions.
+Additionally, this systemizes the format for recording issues for each call, since each topic has a standardized name.
+This ensures topics and departments match across the list, allowing for efficient and accurate analysis.
+Since this is the most recent data and is reflective of the city's current systems, this file was heavily relied upon for analysis on a departmental and topical basis.
 
-	\subsection{Loading Data}
+	\subsection{Loading, Cleaning, \& Preprocessing the Data}
 
-	\subsection{Cleaning Data}
-
-	\subsection{Data Preprocessing}
+This entire analysis was completed using the Anaconda 5.2 distribution of Python 3.6 (Windows 64-bit).
+The data was loaded into 3 separate dataframes through the use of Pandas.
+The data was then inspected for missing data and reasonableness.
+Very little data was missing, with the exception of a small percentage of observations in the case data (the older data).
+Less than 4\% of the 488,601 observations contained missing data.
+These rows were missing a significant proportion of their respective attributes, and thus were dropped completely from the data.
+The daily data was missing no data points.
+The topic data, however, was missing almost 90\% of entries into an attribute titled ``Regarding".
+Since this attribute was of type ``string", a substantial amount was missing, and it was irrelevant to the analysis, it was dropped completely.
+This dataset was missing no other data.
+\par
+Upon reading the CSV files using the Pandas, Python initialized most of the attributes as objects.
+Preprocessing and transforming was conducted immediately to transform the attributes into more useful types, such as date-time and numeric objects.
+Further processing was done throughout the project as necessary in order to provide a useful format.
 

### 2018-08-27 paper.tex
worked on analysis section

@@
 
+The goal of this analysis and visualization task is to, at its core, provide the city of South Bend useful and actionable knowledge about its call center.
+The city was most curious about trends based on time,
+%I dont like that word
+departments, and topics.  Therefore, this analysis has four major analytical focuses:  month of year, day of the week, department, and topic.  
+%I hate everything here
+In order to illustrate the finding in the most information-rich way possible, an interactive graphical dashboard was chosen as the primary means of communication.
+This dashboard is able to be sent throughout the city management conveniently, as it is simply a self-contained HTML file.
+Neither Python nor the data sources are necessary to view and interact with this visualization.
+
 \section{Methods}
+
+	\subsection{Programming \& Packages}
+
+This entire analysis was conducted in Anaconda 5.2 running Python 3.6.4.
+The Python packages used throughout this analysis are all contained within the Anaconda distribution.
+These include Numpy, Pandas, Matplotlib, Scipy, Seaborn, and Bokeh.\cite{python}\cite{anaconda}  The programming and analysis was all conducted using Windows 10 OS.
+The methods and output, however, should be able to work on Python 3.6 (with the required packages) on any OS.
+The code, however, is not backwards-compatible to Python 2.x.
+
+	\subsection{Data}
 
@@
 
-	\subsection{Discuss packages and analysis plan of attack???}
-
 \section{Analysis}
@@
 	\subsection{Calls by Month}
+
+An analysis of call volume by month was conducted using the daily data, which provides aggregate totals by day for a 2-year period.
+The relevant data was manipulated by taking the mean of the daily call volume for every record in each month.
+Upon completion, the data was then plotted in a bar chart format, allowing the user to quickly identify any differences.
+This chart can be viewed in Figure 1.
+
+\begin{figure}[h]
+  \includegraphics[scale=.27]{month_bar.png}
+  \caption{Plot of average daily call volume by month}
+\end{figure}
+
+As an exercise in thoroughness, these findings were subjected to a two-sided t-test for statistical significance.
+The daily call volumes for each month were isolated and stored as lists within a Python dictionary.
+The scipy.stats package was used to conduct the test.
+For the purposes of this test, the null hypothesis stated that ``the two months have identical expected values."  For the null hypothesis to be disproved, a standard threshold p-value of 0.05 was used.
+The heatmap in Figure 2 shows the p-value between each pairing of months.
+From this information, the city can see which months are significantly busier/quieter than others.
+By subjecting the data to such a test, important points can be quickly identified that may or may not be obvious in Figure 1.
+
+\begin{figure}[h]
+	\includegraphics[scale=.65]{Heatmap.png}
+	\caption{P-values resulting from t-test on daily call volume by month}
+\end{figure}
 
@@
 
+One of the primary tasks posed by the city was to explore call trends on a departmental level.
+This was conducted primarily using the topic data, as the data contained accurate and complete information regarding departments.
+In addition to being the most recent, this data also utilizes the new department/topic layout that the city has transitioned to.
+This format includes the knowledge base articles described earlier.
+In this native data format, the department titles were often followed by the characters ``- KB Team".
+Since leaving this suffix appended to each title would only visually detract from the dashboard, the string was removed.
+This process can be seen below:\\
+
+  \begin{Verbatim}[fontsize=\small]
+  for i in range(len(dept)):
+    n = dept[i]
+    dept[i] = n.replace(" - KB Team", "")
+  \end{Verbatim}
+
+Additionally, the time format in the data file was read in as a string.
+Upon investigating, the data was found to have an inconsistent format.
+For example, duration for one record was in the form ``2:34" for two minutes, thirty-four seconds.
+However, for longer calls it could be in the form ``1:15:56" for one hour, fifteen minutes, and fifty-six seconds.
+While beneficial visually, this would not function for any analysis.
+This data was converted into seconds, stored as a numeric data type, using the following function:
+
+  \begin{Verbatim}[fontsize=\small]
+
+def string_to_sec(df, col_name):
+    ''' 
+    This function accepts a dataframe and 
+    column name (in quotes)
+    It converts the column from XX:XX:XX to
+     seconds and returns a list.
+    Pandas must be imported and 
+    aliased as pd
+    '''
+    new = []
+    for i in range(len(df[col_name])):
+        x = df.loc[i][col_name]
+        if x.count(":") == 1:
+            ''' For Min:sec '''
+            y, z = x.split(":")
+            y = pd.to_numeric(y)
+            z = pd.to_numeric(z)
+            q = (y * 60) + z
+        elif x.count(":") == 2:
+       '''For H/Min:Min/sec:Sec/Nothing '''
+            h, y, z = x.split(":")
+            if len(h) == 2:
+                ''' This assumes if the
+               first number is 2 digits,
+               it is minutes'''
+                h = pd.to_numeric(h)
+                y = pd.to_numeric(y)
+                q = (h * 60) + y
+             elif len(h) == 1:
+              '''Assuming first digit is 
+                single, means hours'''
+                h = pd.to_numeric(h)
+                y = pd.to_numeric(y)
+                z = pd.to_numeric(z)
+                q = (h*3600) + (y*60) + z
+             else:
+                 q = np.NaN
+         else:
+              q = np.NaN
+         new.append(q)
+  return new
+  \end{Verbatim}
+
+This function returns a list, which is then evaluated for reasonableness and appended to the dataframe.  By doing this, every call record now has a new attribute for duration in seconds.
+
+Calls by department were then analyzed and visualized by average duration and total volume.
+As expected, the departments' respective ordering in each analysis differed.
+As a more direct approach to the measure of total call volume, the total departmental call times were calculated.
+Of all the approaches, this calculation of total call time may be the most helpful to the city, as this can directly show where time and budget is being spent.
+This visualization can be seen in the pie chart in Figure 3.
+
+\begin{figure}[h]
+  \includegraphics[scale=0.3]{piechart.png}
+  \caption{A visual of total volume by department}
+ \end{figure}
+
 	\subsection{Calls by Topic}
+
+Analyzing calls by topic proved to be one of the most challenging and interesting aspects of this analysis.
+The topic data was used again here due to its recentness and the homogeneity of topic format.
+Among this dataset, 426 unique call topics existed.
+The data was then processed to show total call count and average call duration by topics.
+This data was then merged with a separate dataframe, indexed by topic with department as the only attribute.
+Once completed, the resulting dataframe contained topic, count, average call duration, and corresponding department.
+At this point, the data was ready for analysis.
+
+\subsection{Duration}
+Call duration by topics was calculated in the dataframe creation above, using the ``.groupby()'' method in Pandas.
+However, when the dataframe was sorted to see the quickest and longest average duration, several topics with a low volume rose to the top, some with only one total call.
+In a sense, such records can be viewed as outliers, and were thus removed from reporting in the final dashboard.
+In the end, only topics with a total volume above the first quartile (of total calls) were included in this analysis.
+By reducing the topics analyzed, the call center will be able to focus on topics that take a notable duration to resolve, but that also occur frequently enough to warrant attention.
+This code, however, can be easily adjusted to a different threshold, if management so desires.
+
+\subsection{Volume}
+The total number of calls by topic was then analyzed.
+The dataframe that was used in the previous analysis was again used for this.
+Using the ``.groupby()" method in Pandas in conjunction with ``.count()", the total number of calls for each topic was appended to the dataframe.
+The most frequent call topics were quickly identified, and many showed a significant overlap with the highest volume departments.
+As a result, the volume by topic in and of itself would not serve much use to the city.
+Therefore, the top 7 highest volume departments (identified in Figure 2) were isolated from the rest of the data.
+The individual topics within these departments were then identified.
+By approaching the analysis in this manner, the city can easily see the most popular topics in the busiest departments.
+In order to visualize this data in the most effective manner, a jitterplot was incorporated into the final dashboard.
+This plot can be seen in Figure 4.
+
+\begin{figure}[h]
+  \includegraphics[scale=0.3]{jitterplot.png}
+  \caption{Jitterplot of call volume by topic for the busiest departments.  Hovertool is utilized to show topic.  The topic in diamond is not plotted to scale}
+\end{figure}
 
@@
 
-\begin{thebibliography}{6}
+\begin{thebibliography}{9}
 
-\bibitem{}
+\bibitem{python}
+Python Software Foundation. (2016). Python 3.6. https://docs.python.org/3.6/.
+
+\bibitem{anaconda}
+Anaconda. (2018). Anaconda Distribution 5.2. https://docs.anaconda.com/anaconda/.
 
 \end{thebibliography}
-
-\includepdf[pages=-]{311CallCenterDashboard}
+%\includepdf{311CallCenterDashboard}
 

### 2018-08-28 paper.tex
Restructured paper, new plots being uploaded to github

@@
 
-\section{Analysis}
-
 	\subsection{Calls by Month}
@@
 The relevant data was manipulated by taking the mean of the daily call volume for every record in each month.
-Upon completion, the data was then plotted in a bar chart format, allowing the user to quickly identify any differences.
-This chart can be viewed in Figure 1.
-
-\begin{figure}[h]
-  \includegraphics[scale=.27]{month_bar.png}
-  \caption{Plot of average daily call volume by month}
-\end{figure}
-
 As an exercise in thoroughness, these findings were subjected to a two-sided t-test for statistical significance.
@@
 For the purposes of this test, the null hypothesis stated that ``the two months have identical expected values."  For the null hypothesis to be disproved, a standard threshold p-value of 0.05 was used.
-The heatmap in Figure 2 shows the p-value between each pairing of months.
-From this information, the city can see which months are significantly busier/quieter than others.
-By subjecting the data to such a test, important points can be quickly identified that may or may not be obvious in Figure 1.
 
-\begin{figure}[h]
-	\includegraphics[scale=.65]{Heatmap.png}
-	\caption{P-values resulting from t-test on daily call volume by month}
-\end{figure}
+	\subsection{Calls by Day of Week}
 
-	\subsection{Calls by Day}
+Calls by day of week were able to be obtained from two data files:  daily data and topic data.
+The first conveniently had an attribute consisting of an integer corresponding to a weekday.
+The topic data included a date of call, but it did not have a direct day attribute.
+Such an attribute was able to be created through the use of the ``to\_datetime()" and ``weekday()" functions in Pandas.
+Once this attribute was created in the same format as the daily data, the dataframes were concatonated using ``concat()".
+Aggregate call totals by day were then simply calculated using the ``.count()" method in Pandas.
 
@@
   \begin{Verbatim}[fontsize=\small]
-
  def string_to_sec(df, col_name):
@@
 
-This function returns a list, which is then evaluated for reasonableness and appended to the dataframe.  By doing this, every call record now has a new attribute for duration in seconds.
-
-Calls by department were then analyzed and visualized by average duration and total volume.
-As expected, the departments' respective ordering in each analysis differed.
-As a more direct approach to the measure of total call volume, the total departmental call times were calculated.
-Of all the approaches, this calculation of total call time may be the most helpful to the city, as this can directly show where time and budget is being spent.
-This visualization can be seen in the pie chart in Figure 3.
-
-\begin{figure}[h]
-  \includegraphics[scale=0.3]{piechart.png}
-  \caption{A visual of total volume by department}
- \end{figure}
+This function returns a list, which is then evaluated for reasonableness and appended to the dataframe.  By doing this, every call record now had a new attribute for duration in seconds.
 
@@
 
-Analyzing calls by topic proved to be one of the most challenging and interesting aspects of this analysis.
+Analyzing calls by topic proved to be one of the most challenging aspects of this analysis.
 The topic data was used again here due to its recentness and the homogeneity of topic format.
@@
 Once completed, the resulting dataframe contained topic, count, average call duration, and corresponding department.
-At this point, the data was ready for analysis.
-
-\subsection{Duration}
+At this point, the data was prepared for analysis.
+\par
 Call duration by topics was calculated in the dataframe creation above, using the ``.groupby()'' method in Pandas.
@@
 This code, however, can be easily adjusted to a different threshold, if management so desires.
-
-\subsection{Volume}
+\par
 The total number of calls by topic was then analyzed.
@@
 By approaching the analysis in this manner, the city can easily see the most popular topics in the busiest departments.
-In order to visualize this data in the most effective manner, a jitterplot was incorporated into the final dashboard.
-This plot can be seen in Figure 4.
+
+\section{Analysis}
+
+	\subsection{Calls by Month}
+
+Upon analysis, the months with the highest average daily call volumes were July, April, Jun, and May (in that order).
+The results can be viewed in Figure 1.
+The standard errors for each month (also plotted in Figure 1) do not appear to be so large as to discredit the significance of these differences.
+March, interestingly, has the lowest average volume by a large margin.
+This is especially intriguing since it is immediately prior to what can be seen as the ``busy season".
 
 \begin{figure}[h]
-  \includegraphics[scale=0.3]{jitterplot.png}
+  \includegraphics[scale=.27]{month_bar.png}
+  \caption{Plot of average daily call volume by month}
+\end{figure}
+
+The heatmap in Figure 2 shows the resulting p-value between each pairing of months.
+From this information, the city can see which months are significantly busier/quieter than others.
+By subjecting the data to such a test, important points can be quickly identified that may or may not be obvious in Figure 1.
+For example, June's call volumes are not statistically different from those in April.
+March, however, has a statistically lower daily average than every other month.
+
+\begin{figure}[h]
+	\includegraphics[scale=.5]{Heatmap.png}
+	\caption{P-values resulting from t-test on daily call volume by month}
+\end{figure}
+
+	\subsection{Calls by Day}
+
+The analysis of calls by day of week incorporated over 588,000 calls into the results.
+The output, therefore, can be viewed as information-rich and an excellent measure of call center activity, since the combined data sources span from 2013 into 2018.
+Given the variablity of the vast amount of data, an interactive historgram was chosen as the best method for communication of results.
+The user can click to show/hide days of the week, and the chart will layer the call distributions over each other for comparison.
+Figure 3 shows this graph, with Monday and Thursday visible.
+The general distribution of each day is similar and appears to follow a
+%what the hell kind
+distribution.  Monday has the highest volume distribution, while Friday has the lowest.  This is also evidenced in a swarm plot of only the daily data in Figure 4.
+
+\begin{figure}[h]
+	\includegraphics[scale=.2]{daily_calls.png}
+	\caption{Histogram of total daily calls by day of week, 2013-2018}
+\end{figure}
+
+\begin{figure}[h]
+	\includegraphics[scale=.6]{swarm.png}
+	\caption{Swarmplot of total daily calls by day of week, 2013-2015}
+\end{figure}
+
+	\subsection{Calls by Department}
+
+%analysis here
+Calls by department were analyzed by two measures:  average duration and total volume.
+As expected, the results of each analysis differed.
+Departments such as Solid Waste and Water Works had the highest call volumes, while Code Enforcement and the Mayor's Office has the longest average durations.
+Given this incongruency, it is not immediately clear where the call center's resources are being focused.
+As a more direct approach to the measure of total call volume, the total departmental call times were calculated.
+Of all the approaches, this calculation of total call time may be the most helpful to the city, as this can directly show where time and budget is being spent.
+This visualization can be seen in the pie chart in Figure 5.
+
+\begin{figure}[h]
+  \includegraphics[scale=0.25]{piechart.png}
+  \caption{A visual of total volume by department}
+ \end{figure}
+
+	\subsection{Calls by Topic}
+
+\subsection{Duration}
+
+\subsection{Volume}
+
+In order to visualize this data in the most effective manner, a jitterplot was incorporated into the final dashboard.  This plot can be seen in Figure 6.
+
+\begin{figure}[h]
+  \includegraphics[scale=0.25]{jitterplot.png}
   \caption{Jitterplot of call volume by topic for the busiest departments.  Hovertool is utilized to show topic.  The topic in diamond is not plotted to scale}

### 2018-09-05 paper.tex
maybe last update.  Has to be in word for the journal?
modded paper more

@@
-\documentclass[11pt,twocolumn]{article}
+\documentclass{article}
 \usepackage{graphicx}
@@
 interactive dashboard using the Bokeh library.  In doing so, an interactive HTML file will be distributed to the city, which can then be utilized, modified, and possibly connected 
-directly to the data source}.
+directly to the data source.  Upon completetion, this analysis yielded} %results stuff here
 \end{abstract}
@@
 The city of South Bend, located in northern Indiana, established a citizen-accessible call center in February 2013.
-The call center handles calls from citizens regarding almost every aspect of city interaction, including waste pick-up and removal, water billing and disconnections,
-and code enforcement.  By serving as a central hub for communication, the call center is able to consolidate much of the data regarding citizen/consumer issues.  
-Much of this data is available on South Bend's open data portal at \href{https://data-southbend.opendata.arcgis.com}{https://data-southbend.opendata.arcgis.com}.
-The guiding questions for this analysis included seeking patterns and statistics on call volume and duration by timeframe, department, and topics.
-The city has used several services/formats for data collection, resulting in data sets from differing time periods having different attributes and formats.
-For most of the in-depth topic analysis, the most current format was used.
+The call center handles isues from citizens regarding almost every aspect of city interaction, including waste pick-up and removal, water billing and disconnections,
+and code enforcement.  By serving as a central hub for communication, the call center is able to consolidate a substantial amount of data regarding citizens as consumers.  
+This data is available on South Bend's open data portal at \href{https://data-southbend.opendata.arcgis.com}{https://data-southbend.opendata.arcgis.com}.
 
@@
 The goal of this analysis and visualization task is to, at its core, provide the city of South Bend useful and actionable knowledge about its call center.
-The city was most curious about trends based on time,
-%I dont like that word
-departments, and topics.  Therefore, this analysis has four major analytical focuses:  month of year, day of the week, department, and topic.  
-%I hate everything here
-In order to illustrate the finding in the most information-rich way possible, an interactive graphical dashboard was chosen as the primary means of communication.
-This dashboard is able to be sent throughout the city management conveniently, as it is simply a self-contained HTML file.
-Neither Python nor the data sources are necessary to view and interact with this visualization.
+Given the information-rich nature of this project, an interactive graphical dashboard was chosen as the primary means to communicate results.
+The city was most curious about trends based on time, departments, and topics.
+Therefore, this analysis has four major analytical foci:  month of year, day of the week, department, and topic.
 
 \section{Methods}
-
-	\subsection{Programming \& Packages}
-
-This entire analysis was conducted in Anaconda 5.2 running Python 3.6.4.
-The Python packages used throughout this analysis are all contained within the Anaconda distribution.
-These include Numpy, Pandas, Matplotlib, Scipy, Seaborn, and Bokeh.\cite{python}\cite{anaconda}  The programming and analysis was all conducted using Windows 10 OS.
-The methods and output, however, should be able to work on Python 3.6 (with the required packages) on any OS.
-The code, however, is not backwards-compatible to Python 2.x.
 
@@
 
-This entire analysis was completed using the Anaconda 5.2 distribution of Python 3.6 (Windows 64-bit).
+This entire analysis was completed using the Anaconda 5.2 distribution of Python 3.6.
 The data was loaded into 3 separate dataframes through the use of Pandas.
@@
 
-	\subsection{Calls by Month}
+	\subsection{Methods of Analysis}
 
@@
 Since leaving this suffix appended to each title would only visually detract from the dashboard, the string was removed.
-This process can be seen below:\\
-
-  \begin{Verbatim}[fontsize=\small]
-  for i in range(len(dept)):
-    n = dept[i]
-    dept[i] = n.replace(" - KB Team", "")
-  \end{Verbatim}
-
+\par
 Additionally, the time format in the data file was read in as a string.
@@
 While beneficial visually, this would not function for any analysis.
-This data was converted into seconds, stored as a numeric data type, using the following function:
-
-  \begin{Verbatim}[fontsize=\small]
- def string_to_sec(df, col_name):
-     ''' 
-     This function accepts a dataframe and 
-     column name (in quotes)
-     It converts the column from XX:XX:XX to
-     seconds and returns a list.
-     Pandas must be imported and 
-     aliased as pd
-     '''
-     new = []
-     for i in range(len(df[col_name])):
-         x = df.loc[i][col_name]
-         if x.count(":") == 1:
-            ''' For Min:sec '''
-             y, z = x.split(":")
-             y = pd.to_numeric(y)
-             z = pd.to_numeric(z)
-             q = (y * 60) + z
-         elif x.count(":") == 2:
-          '''For H/Min:Min/sec:Sec/Nothing '''
-             h, y, z = x.split(":")
-            if len(h) == 2:
-             ''' This assumes if the
-               first number is 2 digits,
-               it is minutes'''
-                h = pd.to_numeric(h)
-                y = pd.to_numeric(y)
-                q = (h * 60) + y
-             elif len(h) == 1:
-              '''Assuming first digit is 
-                single, means hours'''
-                h = pd.to_numeric(h)
-                y = pd.to_numeric(y)
-                z = pd.to_numeric(z)
-                q = (h*3600) + (y*60) + z
-             else:
-                q = np.NaN
-         else:
-              q = np.NaN
-         new.append(q)
-  return new
-  \end{Verbatim}
-
-This function returns a list, which is then evaluated for reasonableness and appended to the dataframe.  By doing this, every call record now had a new attribute for duration in seconds.
+This data was converted into seconds, and stored as a numeric data type.
 
@@
 
-Analyzing calls by topic proved to be one of the most challenging aspects of this analysis.
 The topic data was used again here due to its recentness and the homogeneity of topic format.
@@
 
-\begin{figure}[h]
-  \includegraphics[scale=.27]{month_bar.png}
-  \caption{Plot of average daily call volume by month}
-\end{figure}
-
 The heatmap in Figure 2 shows the resulting p-value between each pairing of months.
@@
 March, however, has a statistically lower daily average than every other month.
-
-\begin{figure}[h]
-	\includegraphics[scale=.5]{Heatmap.png}
-	\caption{P-values resulting from t-test on daily call volume by month}
-\end{figure}
 
@@
 Figure 3 shows this graph, with Monday and Thursday visible.
-The general distribution of each day is similar and appears to follow a
+The general call distribution of each day is similar and appears to follow a
 %what the hell kind
@@
 
-\begin{figure}[h]
-	\includegraphics[scale=.2]{daily_calls.png}
-	\caption{Histogram of total daily calls by day of week, 2013-2018}
-\end{figure}
-
-\begin{figure}[h]
-	\includegraphics[scale=.6]{swarm.png}
-	\caption{Swarmplot of total daily calls by day of week, 2013-2015}
-\end{figure}
-
 	\subsection{Calls by Department}
 
-%analysis here
 Calls by department were analyzed by two measures:  average duration and total volume.
@@
 Of all the approaches, this calculation of total call time may be the most helpful to the city, as this can directly show where time and budget is being spent.
-This visualization can be seen in the pie chart in Figure 5.
-
-\begin{figure}[h]
-  \includegraphics[scale=0.25]{piechart.png}
-  \caption{A visual of total volume by department}
- \end{figure}
 
@@
 
-\subsection{Duration}
+Exploration of calls by topic was a priority for the city.
+Within each department, numerous topics exist.
+Given the recent implementation of knowledge base articles (which can be seen in the most recent data), the attachment of topics to each call has been standardized.
+This allows for a simplified, more accurate analysis.
+Calls by topic were specifically analyzed by average duration and total call volume.
+\par
+The %left off here
 
-\subsection{Volume}
-
-In order to visualize this data in the most effective manner, a jitterplot was incorporated into the final dashboard.  This plot can be seen in Figure 6.
-
-\begin{figure}[h]
-  \includegraphics[scale=0.25]{jitterplot.png}
-  \caption{Jitterplot of call volume by topic for the busiest departments.  Hovertool is utilized to show topic.  The topic in diamond is not plotted to scale}
-\end{figure}
+\section{Discussion}
 
@@
 An image of the final dashboard can be found at the end of this paper, while a live link can be followed \href{https://jdbul33.github.io/311_Call_Dashboard.html}{here}.
-
-\section{Discussion}
 
@@
 \end{thebibliography}
-%\includepdf{311CallCenterDashboard}
+\newpage
+
+\begin{figure}[p]
+  \includegraphics[scale=.27]{month_bar.png}
+  \caption{Plot of average daily call volume by month}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[scale=.5]{Heatmap.png}
+	\caption{P-values resulting from t-test on daily call volume by month}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[scale=.35]{daily_calls.png}
+	\caption{Histogram of total daily calls by day of week, 2013-2018}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[scale=.6]{swarm.png}
+	\caption{Swarmplot of total daily calls by day of week, 2013-2015}
+\end{figure}
+
+\begin{figure}[p]
+  \includegraphics[scale=0.25]{jitterplot.png}
+  \caption{Jitterplot of call volume by topic for the busiest departments.  Hovertool is utilized to show topic.  The topic in diamond is not plotted to scale}
+\end{figure}
 

### 2018-09-07 paper.tex
Added, subtracted

@@
 The call center handles isues from citizens regarding almost every aspect of city interaction, including waste pick-up and removal, water billing and disconnections,
-and code enforcement.  By serving as a central hub for communication, the call center is able to consolidate a substantial amount of data regarding citizens as consumers.  
+and code enforcement.
+By serving as a central hub for communication, the call center is able to consolidate a substantial amount of data regarding citizens as consumers.
 This data is available on South Bend's open data portal at \href{https://data-southbend.opendata.arcgis.com}{https://data-southbend.opendata.arcgis.com}.
@@
 The data to be analyzed was acquired in three distinct comma-separated value files.
-Two of the files are publicly available, and are also posted on the \href{https://github.com/jdbul33/verbose-chainsaw}{Github repository} for this project.
-The third file was received directly from the city of South Bend, and as a result is not posted publicly at this time.
-\par
 The first file, referred to as the daily data, contains a daily summary of the call center data from the years 2013-2015.
@@
 \par
-The %left off here
-
-\section{Discussion}
+When ranked by average duration, many obscure topics rose to the extremes.
+Of the top 20 topics with the shortest duration, 19 had a total number of calls of less than three.
+When viewed as a percentage of the total 202,500 call dataset, these calls are such a small proportion that it would give little actionable insight to the city.
+A similar, though less extreme, situation occurred when viewing topics with longest duration.
+\par
+In light of this exploration, it was determined that the most important results for the city to see would include only topics that composed a significant proportion of total calls.
+When ranking by duration, only topics with total volume above the first quartile of total call volume were included.
+This yielded results that could be viewed as more relevant to management.
+Topics with long durations seemed to be centralized around complaints and billing issues, and quick topics were mostly comprised of general information inquiries.
+When analyzed in this manner, there is a 195 second difference between the longest and shortest topics.
+\par
+When topics were ranked in order of total call volume, the top results mostly represented the busiest departments identified earlier, such as Water Works and Solid Waste.
+The top topics included scheduling an extra trash pickup and water line shut-off deadlines.
+Additionally, two of the most voluminous topics were ``Miscellaneous Trash Information" and ``Water Miscellaneous".
+It could be inferred that these two topics serve as a catch-all for the call center.
+By showing management these results, they may be able to discover the true nature of many of these calls, as well as impress the importance of accurate recording by call center operators.
 
@@
 By incorporating these interactions into the dashboard, the result is a more dynamic, engaging product that is simple to interact with for employees outside of the technical fields.
-An image of the final dashboard can be found at the end of this paper, while a live link can be followed \href{https://jdbul33.github.io/311_Call_Dashboard.html}{here}.
+An image of the final dashboard can be found at the end of this paper, while a live link can be accessed at \href{http://jdbul33.github.io/CallCenterDashboard.html}{http://jdbul33.github.io/CallCenterDashboard.html}.
 
@@
 \begin{thebibliography}{9}
-
-\bibitem{python}
-Python Software Foundation. (2016). Python 3.6. https://docs.python.org/3.6/.
-
-\bibitem{anaconda}
-Anaconda. (2018). Anaconda Distribution 5.2. https://docs.anaconda.com/anaconda/.
 

### 2018-09-10 paper.tex
added prior work, added rough results to abstract

@@
 \usepackage{hyperref}
+\usepackage[margin=1.25in]{geometry}
 
@@
 \\
-Karl Schmitt, PhD. (Advisor)
+Karl Schmitt, Ph.D. (Advisor)
 \\
@@
 interactive dashboard using the Bokeh library.  In doing so, an interactive HTML file will be distributed to the city, which can then be utilized, modified, and possibly connected 
-directly to the data source.  Upon completetion, this analysis yielded} %results stuff here
+directly to the data source.
+Upon completetion, this analysis identified insights that could be actionable by the city.
+July was found to be the most voluminous month, which was shown to be statistically signficant through the use of a two-sided t-test.
+Additionally, the departments of Solid Waste and Water Works, along with many of their sub-topics, had some of the highest call volumes.
+When calls were analyzed by duration, however, many lower volume topics were shown to take longer to resolve.}
 \end{abstract}
@@
 	\subsection{Prior Work}
+
+The purpose of this research is to uncover trends and insights that may be of use to call center management.
+Within the scope of this analysis, call duration can be seen as the ``efficiency" measure within this call center, particularly on a topical basis.
+This metric is identified by Baraka et al.
+as one of the primary measures to assess call center success.\cite{baraka}  The authors identify other parameters, but analyzing this operation's success level was not within the scope of this paper.
+\par
+Call center and queueing analysis has been the focus of academic research for years.
+Brown et al.
+provide an excellent overview of the Poisson distribution modeling customer arrivals, as well as the accompanying assumptions.
+While arrival distribution is not analyzed in this paper, the authors' assumptions are, for the most part, assumed to be true in this analysis.
+These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as neglegible.
 
@@
 
-	\subsection{Methods of Analysis}
+	\subsection{Calls by Month}
 
@@
 
-\begin{thebibliography}{9}
+\begin{thebibliography}{2}
+
+\bibitem{baraka}
+Baraka, H., Baraka H. \& El-Gamily, I. (2013). Assessing call centers' success: A validation of the DeLone and Mclean model for information system. \textit{Egyptian Informatics Journal, 14}, 99-108.
+
+\bibitem{brown}
+Brown, L., Gans, N., Mandelbaum, A., Sakov, A., Shen, H., Zeltyn, S., \& Zhao, L.
+(2005).
+Statistical analysis of a telephone call center: a queueing-science perspective.
+\textit{Journal of the American Statistical Association, 100(469)}, 36-50.
 

### 2018-09-11 paper.tex
Made revisions from meeting 9/11

@@
 The city of South Bend, located in northern Indiana, established a citizen-accessible call center in February 2013.
-The call center handles isues from citizens regarding almost every aspect of city interaction, including waste pick-up and removal, water billing and disconnections,
+They address almost every aspect of city-citizen interaction, including waste pick-up and removal, water billing and disconnections,
 and code enforcement.
@@
 The city was most curious about trends based on time, departments, and topics.
-Therefore, this analysis has four major analytical foci:  month of year, day of the week, department, and topic.
+Therefore, this project had four major analytical foci:  month of year, day of the week, department, and topic.
 
-\section{Methods}
+\section{Data}
 
-	\subsection{Data}
-
-The data to be analyzed was acquired in three distinct comma-separated value files.
-The first file, referred to as the daily data, contains a daily summary of the call center data from the years 2013-2015.
+The data to be analyzed was acquired in three distinct files.
+\par
+\textbf{Daily Data --} contains a daily summary of the call center data from the years 2013-2015.
 It is organized with 637 records indexed by date, with each record containing information such as the number of calls presented, average wait time, average number of calls in queue, and number of abandoned calls for that day.
 \par
-The second file, referred to as the case data, contains 488,601 rows of individual call data from 2013 through 2015.
+\textbf{Case Data --} contains 488,601 rows of individual call data from 2013 through 2015.
 Calls were logged anonymously with data such as date, duration, topic, and department.
@@
 \par
-The third file, referred to as the topic data, is the storage method of the current phone system in use by the city.
-This file contains 202,500 call records from 2016-2018.
-It contains much of the same attributes as the case data, but it is standardized to reflect the city's use of knowledge base articles.
-These articles correspond to possible questions or issues raised by callers; as a result, the call center employees have a reference to answer questions.
-Additionally, this systemizes the format for recording issues for each call, since each topic has a standardized name.
+\textbf{Topic Data --} contains many of the same attributes as the case data, but it reflects the city's current use of knowledge base articles.
+This systemizes the format for recording issues for each call, since each topic has a standardized name.
 This ensures topics and departments match across the list, allowing for efficient and accurate analysis.
-Since this is the most recent data and is reflective of the city's current systems, this file was heavily relied upon for analysis on a departmental and topical basis.
+\par
+The data was then inspected for missing data and reasonableness.
+The daily data was missing no data points.
+In the case data, less than 4\% of the 488,601 observations contained missing data.
+These rows were missing a significant proportion of their respective attributes, and thus were dropped completely from the data.
+The topic data, however, was missing almost 90\% of entries into an attribute used for open-format comments.
+Since a substantial amount was missing and it was irrelevant to the analysis, this attribute was dropped completely.
+This dataset was missing no other data.
+Preprocessing and transformation was conducted immediately to transform the attributes into more useful types, such as date-time and numeric objects.
 
-	\subsection{Loading, Cleaning, \& Preprocessing the Data}
+\section{Analytical Methods}
 
-This entire analysis was completed using the Anaconda 5.2 distribution of Python 3.6.
-The data was loaded into 3 separate dataframes through the use of Pandas.
-The data was then inspected for missing data and reasonableness.
-Very little data was missing, with the exception of a small percentage of observations in the case data (the older data).
-Less than 4\% of the 488,601 observations contained missing data.
-These rows were missing a significant proportion of their respective attributes, and thus were dropped completely from the data.
-The daily data was missing no data points.
-The topic data, however, was missing almost 90\% of entries into an attribute titled ``Regarding".
-Since this attribute was of type ``string", a substantial amount was missing, and it was irrelevant to the analysis, it was dropped completely.
-This dataset was missing no other data.
-\par
-Upon reading the CSV files using the Pandas, Python initialized most of the attributes as objects.
-Preprocessing and transforming was conducted immediately to transform the attributes into more useful types, such as date-time and numeric objects.
-Further processing was done throughout the project as necessary in order to provide a useful format.
-
-	\subsection{Calls by Month}
-
-An analysis of call volume by month was conducted using the daily data, which provides aggregate totals by day for a 2-year period.
+\textbf{Call volume by month --} was conducted using the daily data, which provides aggregate totals by day for a 2-year period.
 The relevant data was manipulated by taking the mean of the daily call volume for every record in each month.
 As an exercise in thoroughness, these findings were subjected to a two-sided t-test for statistical significance.
-The daily call volumes for each month were isolated and stored as lists within a Python dictionary.
-The scipy.stats package was used to conduct the test.
 For the purposes of this test, the null hypothesis stated that ``the two months have identical expected values."  For the null hypothesis to be disproved, a standard threshold p-value of 0.05 was used.
-
-	\subsection{Calls by Day of Week}
-
-Calls by day of week were able to be obtained from two data files:  daily data and topic data.
+\par
+\textbf{Call volume by day of the week --} was conducted from data contained in two files: daily data and topic data.
 The first conveniently had an attribute consisting of an integer corresponding to a weekday.
 The topic data included a date of call, but it did not have a direct day attribute.
-Such an attribute was able to be created through the use of the ``to\_datetime()" and ``weekday()" functions in Pandas.
-Once this attribute was created in the same format as the daily data, the dataframes were concatonated using ``concat()".
-Aggregate call totals by day were then simply calculated using the ``.count()" method in Pandas.
-
-	\subsection{Calls by Department}
-
-One of the primary tasks posed by the city was to explore call trends on a departmental level.
-This was conducted primarily using the topic data, as the data contained accurate and complete information regarding departments.
-In addition to being the most recent, this data also utilizes the new department/topic layout that the city has transitioned to.
-This format includes the knowledge base articles described earlier.
-In this native data format, the department titles were often followed by the characters ``- KB Team".
-Since leaving this suffix appended to each title would only visually detract from the dashboard, the string was removed.
+This attributed was created with the same format as the daily data, and the calls corresponding to each date were counted.
+The two dataframes were then concantenated, providing the total number of calls for each date.
+Once grouped by weekday, this yielded a distribution of total calls for each day of the week over a five year period.
 \par
-Additionally, the time format in the data file was read in as a string.
-Upon investigating, the data was found to have an inconsistent format.
+\textbf{Calls volume and duration by department --} were analyzed using the topic data, as the data contained recent and complete information regarding departments.
+One major impediment in this data was the format of call duration, which did not utilize a fixed-length field.
 For example, duration for one record was in the form ``2:34" for two minutes, thirty-four seconds.
@@
 While beneficial visually, this would not function for any analysis.
-This data was converted into seconds, and stored as a numeric data type.
-
-	\subsection{Calls by Topic}
-
-The topic data was used again here due to its recentness and the homogeneity of topic format.
+The duration was converted into seconds, and stored as a numeric data type.
+\par
+\textbf{Call volume and duration by topic --} were analyzed from the topic data as well.
 Among this dataset, 426 unique call topics existed.
 The data was then processed to show total call count and average call duration by topics.
-This data was then merged with a separate dataframe, indexed by topic with department as the only attribute.
-Once completed, the resulting dataframe contained topic, count, average call duration, and corresponding department.
-At this point, the data was prepared for analysis.
-\par
-Call duration by topics was calculated in the dataframe creation above, using the ``.groupby()'' method in Pandas.
-However, when the dataframe was sorted to see the quickest and longest average duration, several topics with a low volume rose to the top, some with only one total call.
-In a sense, such records can be viewed as outliers, and were thus removed from reporting in the final dashboard.
-In the end, only topics with a total volume above the first quartile (of total calls) were included in this analysis.
-By reducing the topics analyzed, the call center will be able to focus on topics that take a notable duration to resolve, but that also occur frequently enough to warrant attention.
-This code, however, can be easily adjusted to a different threshold, if management so desires.
-\par
-The total number of calls by topic was then analyzed.
-The dataframe that was used in the previous analysis was again used for this.
-Using the ``.groupby()" method in Pandas in conjunction with ``.count()", the total number of calls for each topic was appended to the dataframe.
-The most frequent call topics were quickly identified, and many showed a significant overlap with the highest volume departments.
-As a result, the volume by topic in and of itself would not serve much use to the city.
-Therefore, the top 7 highest volume departments (identified in Figure 2) were isolated from the rest of the data.
-The individual topics within these departments were then identified.
-By approaching the analysis in this manner, the city can easily see the most popular topics in the busiest departments.
+Once completed, the data was able to be sorted by volume and duration, allowing for one dataset to serve the purposes of analysis of both duration and volume.
 

### 2018-09-20 paper.tex
Cleaned up some analysis, need to change headings and layout a bit

@@
 
-Upon analysis, the months with the highest average daily call volumes were July, April, Jun, and May (in that order).
+Upon analysis, the months with the highest average daily call volumes were July, April, June, and May (in that order).
 The results can be viewed in Figure 1.
-The standard errors for each month (also plotted in Figure 1) do not appear to be so large as to discredit the significance of these differences.
+The standard errors for each month (also plotted in Figure 1) appear to be small enough the significance of these differences.
 March, interestingly, has the lowest average volume by a large margin.
@@
 The heatmap in Figure 2 shows the resulting p-value between each pairing of months.
-From this information, the city can see which months are significantly busier/quieter than others.
-By subjecting the data to such a test, important points can be quickly identified that may or may not be obvious in Figure 1.
-For example, June's call volumes are not statistically different from those in April.
+An interesting point that appears is that June's call volumes are not statistically different from those in April.
 March, however, has a statistically lower daily average than every other month.
@@
 The analysis of calls by day of week incorporated over 588,000 calls into the results.
-The output, therefore, can be viewed as information-rich and an excellent measure of call center activity, since the combined data sources span from 2013 into 2018.
-Given the variablity of the vast amount of data, an interactive historgram was chosen as the best method for communication of results.
-The user can click to show/hide days of the week, and the chart will layer the call distributions over each other for comparison.
 Figure 3 shows this graph, with Monday and Thursday visible.
@@
 Calls by department were analyzed by two measures:  average duration and total volume.
-As expected, the results of each analysis differed.
-Departments such as Solid Waste and Water Works had the highest call volumes, while Code Enforcement and the Mayor's Office has the longest average durations.
+Departments such as Solid Waste and Water Works had the highest call volumes, while Code Enforcement and the Mayor's Office had the longest average durations.
 Given this incongruency, it is not immediately clear where the call center's resources are being focused.
 As a more direct approach to the measure of total call volume, the total departmental call times were calculated.
-Of all the approaches, this calculation of total call time may be the most helpful to the city, as this can directly show where time and budget is being spent.
+%add plot here
 

### 2018-09-24 paper.tex
prior work, new charts, condensed some analysis

@@
 While arrival distribution is not analyzed in this paper, the authors' assumptions are, for the most part, assumed to be true in this analysis.
-These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as neglegible.
+These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also descibe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.
+As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as neglegible.
+\par
+Prior work with call centers often centers around simulation.
+According to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.
+For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  This could be viewed as a logical next step for this project, with this work discovering the baseline knowedge necessary to construct such a model.
 
@@
 
-	\subsection{Calls by Month}
-
-Upon analysis, the months with the highest average daily call volumes were July, April, June, and May (in that order).
+\textbf{Call volume by month --} was analyzed using the daily data.
+Months with the highest average daily call volumes were July, April, June, and May (in that order).
 The results can be viewed in Figure 1.
@@
 March, however, has a statistically lower daily average than every other month.
+\par
 
-	\subsection{Calls by Day}
+\textbf{Call volume by day of the week --} incorporated over 588,000 calls into the results.
+In order to most clearly see the results, a series of boxplots are shown in Figure 2.
+Upon evaluation, call volume trends highest on Monday, then steadily decreases as the work week continues on.
+The 311 service allows for voicemails to be left after hours, allowing operators to call customers back during business hours.
+This could be a reason for the higher number of calls on Monday and Tuesday, since a weekend's worth of calls are presumably being dealt with.
+\par
 
-The analysis of calls by day of week incorporated over 588,000 calls into the results.
-Figure 3 shows this graph, with Monday and Thursday visible.
-The general call distribution of each day is similar and appears to follow a
-%what the hell kind
-distribution.  Monday has the highest volume distribution, while Friday has the lowest.  This is also evidenced in a swarm plot of only the daily data in Figure 4.
-
-	\subsection{Calls by Department}
-
-Calls by department were analyzed by two measures:  average duration and total volume.
+\textbf{Calls by department --} were analyzed by two measures:  average duration and total volume.
 Departments such as Solid Waste and Water Works had the highest call volumes, while Code Enforcement and the Mayor's Office had the longest average durations.
@@
 As a more direct approach to the measure of total call volume, the total departmental call times were calculated.
-%add plot here
+This can be visualized in Figure 4.
+\par
 
-	\subsection{Calls by Topic}
-
-Exploration of calls by topic was a priority for the city.
+\textbf{Calls by topic --} were also analyzed by duration and volume.
 Within each department, numerous topics exist.
@@
 This allows for a simplified, more accurate analysis.
-Calls by topic were specifically analyzed by average duration and total call volume.
 \par
@@
 A similar, though less extreme, situation occurred when viewing topics with longest duration.
-\par
 In light of this exploration, it was determined that the most important results for the city to see would include only topics that composed a significant proportion of total calls.
@@
 When analyzed in this manner, there is a 195 second difference between the longest and shortest topics.
+% should this be better?
+Graph?
 \par
@@
 By showing management these results, they may be able to discover the true nature of many of these calls, as well as impress the importance of accurate recording by call center operators.
+Since the most popular topics were representative of the busiest departments, these were visualized in tandem.
+The jitterplot in Figure 5 shows the call volume for individual topics within some of the cities busiest departments.
 
-	\subsection{Final Dashboard}
+\section{Discussion}
 
-After completion of the above analysis, the final dashboard was constructed.
-Each chart in this dashboard stems from a question or interest identified by the city analysts.
-The Bokeh package was used to create interactive visualizations, and allowed the final product to be conveniently packaged into a HTML file and sent to the call center management.
+While the above analysis yielded clear results, the call center did not have any specific questions for which it was seeking answers.
+Instead, this project was geared towards discovering trends, patterns, and insights; these were then provided to the city so that they could formulate specific questions based on the story that was told by this data.
+In order to provide this to city managment, a visualization dashboard was chosn as the most effective medium.
+The Bokeh package was used to create interactive visualizations, and allowed the final product to be packaged into a HTML file and sent to the call center management.
 In all, the dashboard includes visualizations of:
@@
 Several paths for further work on this topic exist; however, the exact approach depends on the city's desires.
-One approach would be to obtain staffing and scheduling information for the call center and use simulation and optimization techniques to evaluate staffing levels and efficiency.
-Another approach would be to develop another dashboard, or perhaps modify the current one, to interact directly with the call center's data source.
+Currently, this data is being expanded into a model that will run as a simulation to determine the effectiveness of the call center.
+This research provides much insight into distribution of topics and their average by each day of the week.
+The data used in this analysis can also be explored from the angle of creating a simulation.
+By simply obtaining a weekly operator schedule from the city, an effective simulation can be built to evaluate staffing levels, customer satisfaction, and many other call center metrics.
+\par
+Another possible approach would be to develop another dashboard, or perhaps modify the current one, to interact directly with the call center's data source.
 This would allow a live, current view of trending topics and departments.
@@
 
-\begin{thebibliography}{2}
+\begin{thebibliography}{5}
 
@@
 \textit{Journal of the American Statistical Association, 100(469)}, 36-50.
+
+\bibitem{zhang}
+Xiaowei Zhang, L.
+Jeff Hong, \& Jiheng Zhang.
+(2014).
+Scaling and modeling of call center arrivals.
+\textit{In Proceedings of the 2014 Winter Simulation Conference (WSC '14)}.
+IEEE Press, Piscataway, NJ, USA, 476-485.
+
+\bibitem{bapat}
+Vivek Bapat \& Eddie B.
+Pruitte, Jr..
+(1998).
+Using simulation in call centers.
+\textit{In Proceedings of the 30th conference on Winter simulation (WSC '98)}, D.
+J.
+Medeiros, Edward F.
+Watson, John S.
+Carson, and Mani S.
+Manivannan (Eds.).
+IEEE Computer Society Press, Los Alamitos, CA, USA, 1395-1400.
+
+\bibitem{saltzman}
+Robert Saltzman \& Vijay Mehrotra.
+(2007).
+Managing trade-offs in call center agent scheduling: methodology and case study.
+\textit{In Proceedings of the 2007 Summer Computer Simulation Conference (SCSC '07)}.
+Society for Computer Simulation International, San Diego, CA, USA, 643-651.
 
@@
 \begin{figure}[p]
-	\includegraphics[scale=.35]{daily_calls.png}
-	\caption{Histogram of total daily calls by day of week, 2013-2018}
+	\includegraphics[scale=.6]{Daily_Call_Boxplot.png}
+	\caption{Total daily calls by day of week, 2013-2018}
 \end{figure}
@@
 \begin{figure}[p]
-	\includegraphics[scale=.6]{swarm.png}
-	\caption{Swarmplot of total daily calls by day of week, 2013-2015}
+	\includegraphics[scale=.6]{Calls_Department.png}
+	\caption{Total Time Spent on Calls by Top Departments, 2016-2018}
 \end{figure}

### 2018-09-27 paper.tex
cleaned up plots and stuff, paper doesnt reflect new plots yet

@@
 The city of South Bend, located in northern Indiana, established a citizen-accessible call center in February 2013.
-They address almost every aspect of city-citizen interaction, including waste pick-up and removal, water billing and disconnections,
+It addresses almost every aspect of city-citizen interaction, including waste pick-up and removal, water billing and disconnections,
 and code enforcement.
@@
 \par
-Prior work with call centers often centers around simulation.
-According to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.
+Call centers are a prime opportunity to utilize simulation techniques.
+In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.
 For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  This could be viewed as a logical next step for this project, with this work discovering the baseline knowedge necessary to construct such a model.
@@
 This is especially intriguing since it is immediately prior to what can be seen as the ``busy season".
-
-The heatmap in Figure 2 shows the resulting p-value between each pairing of months.
+The heatmap in Figure 2 shows the resulting p-value from the t-test between each pair of months' distributions.
 An interesting point that appears is that June's call volumes are not statistically different from those in April.

### 2018-09-28 paper.tex
paper incorporates new plots

@@
 Once grouped by weekday, this yielded a distribution of total calls for each day of the week over a five year period.
+This data was also subjected to a t-test as monthly call volume was.
 \par
@@
 The results can be viewed in Figure 1.
-The standard errors for each month (also plotted in Figure 1) appear to be small enough the significance of these differences.
 March, interestingly, has the lowest average volume by a large margin.
@@
 \textbf{Call volume by day of the week --} incorporated over 588,000 calls into the results.
-In order to most clearly see the results, a series of boxplots are shown in Figure 2.
+In order to most clearly see the results, a series of boxplots are shown in Figure 3.
 Upon evaluation, call volume trends highest on Monday, then steadily decreases as the work week continues on.
@@
 This could be a reason for the higher number of calls on Monday and Tuesday, since a weekend's worth of calls are presumably being dealt with.
+A heatmap is shown in Figure 4, which emphasizes the statistically different mean for each pairing of weekdays (with the exception of Wednesday and Thursday).
 \par
@@
 \textbf{Calls by topic --} were also analyzed by duration and volume.
-Within each department, numerous topics exist.
-Given the recent implementation of knowledge base articles (which can be seen in the most recent data), the attachment of topics to each call has been standardized.
-This allows for a simplified, more accurate analysis.
-\par
 When ranked by average duration, many obscure topics rose to the extremes.
@@
 When analyzed in this manner, there is a 195 second difference between the longest and shortest topics.
-% should this be better?
-Graph?
 \par
-When topics were ranked in order of total call volume, the top results mostly represented the busiest departments identified earlier, such as Water Works and Solid Waste.
-The top topics included scheduling an extra trash pickup and water line shut-off deadlines.
-Additionally, two of the most voluminous topics were ``Miscellaneous Trash Information" and ``Water Miscellaneous".
-It could be inferred that these two topics serve as a catch-all for the call center.
-By showing management these results, they may be able to discover the true nature of many of these calls, as well as impress the importance of accurate recording by call center operators.
-Since the most popular topics were representative of the busiest departments, these were visualized in tandem.
-The jitterplot in Figure 5 shows the call volume for individual topics within some of the cities busiest departments.
+Topic volume was dominated by topics within many of the top departments identified earlier in Figure 1.
+The top two highest volume topics, by a large margin, were ``Miscellaneous Trash Information" and ``Water Miscellaneous".
+This is reflective of positions of Solid Waste and Water Works in the departmental analysis.
+In order to allow the city to effectively visualize this tandem effect, topics within the some of the busiest departments were plotted in an interactive jitterplot, as seen in Figure 4.
 
@@
 \begin{figure}[p]
-  \includegraphics[scale=.27]{month_bar.png}
-  \caption{Plot of average daily call volume by month}
+  \includegraphics[scale=.6]{monthly_boxplot.png}
+  \caption{Distribution of average daily call volume by month}
 \end{figure}
@@
 	\includegraphics[scale=.6]{Daily_Call_Boxplot.png}
-	\caption{Total daily calls by day of week, 2013-2018}
+	\caption{Total daily calls by day of week}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[scale=.5]{Daily_Heatmap.png}
+	\caption{P-values resulting from t-test on daily call volume by day of the week}
 \end{figure}

### 2018-10-01 paper.tex
fixed some Typos

@@
 directly to the data source.
-Upon completetion, this analysis identified insights that could be actionable by the city.
-July was found to be the most voluminous month, which was shown to be statistically signficant through the use of a two-sided t-test.
+Upon completion, this analysis identified insights that could be actionable by the city.
+July was found to be the most voluminous month, which was shown to be statistically significant through the use of a two-sided t-test.
 Additionally, the departments of Solid Waste and Water Works, along with many of their sub-topics, had some of the highest call volumes.
@@
 \par
-Call center and queueing analysis has been the focus of academic research for years.
+Call center and queuing analysis has been the focus of academic research for years.
 Brown et al.
@@
 While arrival distribution is not analyzed in this paper, the authors' assumptions are, for the most part, assumed to be true in this analysis.
-These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also descibe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.
-As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as neglegible.
+These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also describe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.
+As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as negligible.
 \par
@@
 In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.
-For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  This could be viewed as a logical next step for this project, with this work discovering the baseline knowedge necessary to construct such a model.
+For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  This could be viewed as a logical next step for this project, with this work discovering the baseline knowledge necessary to construct such a model.
 
@@
 When ranked by average duration, many obscure topics rose to the extremes.
-Of the top 20 topics with the shortest duration, 19 had a total number of calls of less than three.
+Of the top 20 topics with the shortest duration, 19 consisted of less than three total calls.
 When viewed as a percentage of the total 202,500 call dataset, these calls are such a small proportion that it would give little actionable insight to the city.
@@
 Instead, this project was geared towards discovering trends, patterns, and insights; these were then provided to the city so that they could formulate specific questions based on the story that was told by this data.
-In order to provide this to city managment, a visualization dashboard was chosn as the most effective medium.
+In order to provide this to city management, a visualization dashboard was chosen as the most effective medium.
 The Bokeh package was used to create interactive visualizations, and allowed the final product to be packaged into a HTML file and sent to the call center management.

### 2018-10-16 paper.tex
advisor fixes made

@@
 analyzed for patterns by time of year, department, and topics with varying methods.  The cleaned, manipulated, and explored data was then developed into an 
-interactive dashboard using the Bokeh library.  In doing so, an interactive HTML file will be distributed to the city, which can then be utilized, modified, and possibly connected 
+interactive dashboard using the Bokeh library.  An interactive HTML file was be distributed to the city, which can then be utilized, modified, and possibly connected 
 directly to the data source.
-Upon completion, this analysis identified insights that could be actionable by the city.
+This analysis discovered insights that are of interest to the city.
 July was found to be the most voluminous month, which was shown to be statistically significant through the use of a two-sided t-test.
@@
 The city of South Bend, located in northern Indiana, established a citizen-accessible call center in February 2013.
-It addresses almost every aspect of city-citizen interaction, including waste pick-up and removal, water billing and disconnections,
+This center addresses almost every aspect of city-citizen interaction, including waste pick-up and removal, water billing and disconnections,
 and code enforcement.
@@
 This data is available on South Bend's open data portal at \href{https://data-southbend.opendata.arcgis.com}{https://data-southbend.opendata.arcgis.com}.
-
-	\subsection{Prior Work}
-
-The purpose of this research is to uncover trends and insights that may be of use to call center management.
-Within the scope of this analysis, call duration can be seen as the ``efficiency" measure within this call center, particularly on a topical basis.
-This metric is identified by Baraka et al.
-as one of the primary measures to assess call center success.\cite{baraka}  The authors identify other parameters, but analyzing this operation's success level was not within the scope of this paper.
-\par
-Call center and queuing analysis has been the focus of academic research for years.
-Brown et al.
-provide an excellent overview of the Poisson distribution modeling customer arrivals, as well as the accompanying assumptions.
-While arrival distribution is not analyzed in this paper, the authors' assumptions are, for the most part, assumed to be true in this analysis.
-These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also describe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.
-As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as negligible.
-\par
-Call centers are a prime opportunity to utilize simulation techniques.
-In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.
-For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  This could be viewed as a logical next step for this project, with this work discovering the baseline knowledge necessary to construct such a model.
 
@@
 
+	\subsection{Prior Work}
+
+The purpose of this research is to uncover trends and insights that may be of use to call center management.
+Within the scope of this analysis, call duration can be seen as the ``efficiency" measure within this call center, particularly on a topical basis.
+This metric is identified by Baraka et al.
+as one of the primary measures to assess call center success.\cite{baraka}  The authors identify other parameters, but call duration is one of the two primary foci of this analysis.
+\par
+Call center and queuing analysis has been the focus of academic research for years.
+While this analysis does not address or explore any incoming call distribution, it is nevertheless important to examine in any call center study.
+Brown et al.
+provide an excellent overview of the Poisson distribution for modeling customer arrivals (in this case, incoming calls to the call center).
+The authors also discuss necessary accompanying assumptions for this arrival distribution to hold true.
+Of these, the assumption that customers and operators are statistically identical and that they all act independently are most important in this analysis.\cite{brown}  Zhang, Hong, and Zhang also describe the arrivals as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.
+As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as negligible in this analysis.
+\par
+Call centers are a prime opportunity to utilize simulation techniques.
+In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.
+For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  This could be viewed as a logical next step for this project, with this work discovering the baseline knowledge necessary to construct such a model.
+
 \section{Data}
@@
 \textbf{Daily Data --} contains a daily summary of the call center data from the years 2013-2015.
-It is organized with 637 records indexed by date, with each record containing information such as the number of calls presented, average wait time, average number of calls in queue, and number of abandoned calls for that day.
+It is organized with 637 records indexed by date, with each record containing information such as the number of calls received, average wait time, average number of calls in queue, and number of abandoned calls for that day.
 \par
@@
 \par
-The data was then inspected for missing data and reasonableness.
+After loading the data, it was then inspected for missing data and reasonableness.
 The daily data was missing no data points.
@@
 These rows were missing a significant proportion of their respective attributes, and thus were dropped completely from the data.
-The topic data, however, was missing almost 90\% of entries into an attribute used for open-format comments.
+The topic data, however, was missing almost 90\% of entries in an attribute used for open-format comments.
 Since a substantial amount was missing and it was irrelevant to the analysis, this attribute was dropped completely.
@@
 
-\textbf{Call volume by month --} was conducted using the daily data, which provides aggregate totals by day for a 2-year period.
+\textbf{Call volume by month --} was analyzed using the daily data, which provides aggregate totals by day for a 2-year period.
 The relevant data was manipulated by taking the mean of the daily call volume for every record in each month.
@@
 \par
-\textbf{Call volume by day of the week --} was conducted from data contained in two files: daily data and topic data.
+\textbf{Call volume by day of the week --} was analyzed using data contained in two files: daily data and topic data.
 The first conveniently had an attribute consisting of an integer corresponding to a weekday.
@@
 This attributed was created with the same format as the daily data, and the calls corresponding to each date were counted.
-The two dataframes were then concantenated, providing the total number of calls for each date.
+The two dataframes were then concatenated, providing the total number of calls for each date.
 Once grouped by weekday, this yielded a distribution of total calls for each day of the week over a five year period.
-This data was also subjected to a t-test as monthly call volume was.
+This data was also subjected to a t-test, in order to determine if the days statistically differed in calls received from each other.
+As in the t-test for call volume by month, a 0.05 threshold was used for the p-value.
 \par
-\textbf{Calls volume and duration by department --} were analyzed using the topic data, as the data contained recent and complete information regarding departments.
-One major impediment in this data was the format of call duration, which did not utilize a fixed-length field.
-For example, duration for one record was in the form ``2:34" for two minutes, thirty-four seconds.
-However, for longer calls it could be in the form ``1:15:56" for one hour, fifteen minutes, and fifty-six seconds.
-While beneficial visually, this would not function for any analysis.
-The duration was converted into seconds, and stored as a numeric data type.
+\textbf{Call volume and duration by department --} were analyzed using the topic data, as the data contained recent and complete information regarding departments.
+The calls were aggregated by department, using total calls received and mean duration in order to compare departments.
 \par
@@
 Among this dataset, 426 unique call topics existed.
-The data was then processed to show total call count and average call duration by topics.
-Once completed, the data was able to be sorted by volume and duration, allowing for one dataset to serve the purposes of analysis of both duration and volume.
+The calls were grouped by topic using total calls received and mean duration in order to facilitate comparison.
 
-\section{Analysis}
+\section{Results}
 
-\textbf{Call volume by month --} was analyzed using the daily data.
+\textbf{Call volume by month --} can be observed in the boxplots in Figure 1.
 Months with the highest average daily call volumes were July, April, June, and May (in that order).
-The results can be viewed in Figure 1.
 March, interestingly, has the lowest average volume by a large margin.
 This is especially intriguing since it is immediately prior to what can be seen as the ``busy season".
-The heatmap in Figure 2 shows the resulting p-value from the t-test between each pair of months' distributions.
+The heatmap in Figure 2 shows the resulting p-value from the two tailed t-test between each pair of months' distributions.
 An interesting point that appears is that June's call volumes are not statistically different from those in April.
-March, however, has a statistically lower daily average than every other month.
+March, however, has a statistically different daily average than every other month.
 \par
 
-\textbf{Call volume by day of the week --} incorporated over 588,000 calls into the results.
-In order to most clearly see the results, a series of boxplots are shown in Figure 3.
+\textbf{Call volume by day of the week --} can be compared in the boxplots in Figure 3.
 Upon evaluation, call volume trends highest on Monday, then steadily decreases as the work week continues on.
-The 311 service allows for voicemails to be left after hours, allowing operators to call customers back during business hours.
-This could be a reason for the higher number of calls on Monday and Tuesday, since a weekend's worth of calls are presumably being dealt with.
+The call center is not open on the weekend, so this could be a reason for the higher number of calls on Monday and Tuesday.
+Presumably, customers would call early in the week to address any issues that arose over the weekend.
 A heatmap is shown in Figure 4, which emphasizes the statistically different mean for each pairing of weekdays (with the exception of Wednesday and Thursday).
@@
 This yielded results that could be viewed as more relevant to management.
-Topics with long durations seemed to be centralized around complaints and billing issues, and quick topics were mostly comprised of general information inquiries.
+Topics with long durations seemed to be centralized around complaints and billing issues, and topics with a short mean duration were mostly comprised of general information inquiries.
 When analyzed in this manner, there is a 195 second difference between the longest and shortest topics.
@@
 
-\section{Discussion}
+\section{Project Outcomes}
 
@@
 Statistical analysis of a telephone call center: a queueing-science perspective.
-\textit{Journal of the American Statistical Association, 100(469)}, 36-50.
+\textit{Journal of the American Statistical Association, 100}(469), 36-50.
 
 \bibitem{zhang}
-Xiaowei Zhang, L.
+Zhang X., L.
 Jeff Hong, \& Jiheng Zhang.
@@
 \bibitem{bapat}
-Vivek Bapat \& Eddie B.
-Pruitte, Jr..
+Bapat, V.
+\& Pruitte, E.B.
+Jr..
 (1998).
@@
 \bibitem{saltzman}
-Robert Saltzman \& Vijay Mehrotra.
+Saltzman, R.
+\& Mehrotra, V..
 (2007).

### 2018-11-08 paper.tex
added stuff, paper no longer up to date, now in word for submission purposes

@@
 The call center handles topics for nearly all of the city's departments.
-An open data portal, maintained by the city, contains several years worth of information.
+An open data portal, maintained by the city, contains several years' worth of information.
 An analysis of this data was conducted using Python 3.6.
@@
 This dataset was missing no other data.
-Preprocessing and transformation was conducted immediately to transform the attributes into more useful types, such as date-time and numeric objects.
+Preprocessing and transformation were conducted immediately to transform the attributes into more useful types, such as date-time and numeric objects.
 
@@
 In order to provide this to city management, a visualization dashboard was chosen as the most effective medium.
-The Bokeh package was used to create interactive visualizations, and allowed the final product to be packaged into a HTML file and sent to the call center management.
+The Bokeh package was used to create interactive visualizations and allowed the final product to be packaged into a HTML file and sent to the call center management.
 In all, the dashboard includes visualizations of:
